Ecological footprint

### 2021-05-22 eco_footprint.Rmd
update missing values analysis

---
title: "Ecological footprint"
author: "Juan Rocha"
date: "4/26/2021"
output: html_document
---

@@

```{r}
ecofp
```

>>>>

---
title: "Ecological footprint"
author: "Juan Rocha"
date: "4/26/2021"
output:
  html_notebook:
      theme:
          code_font:
            google: Fira Code
---

@@

```{r}
ecofp

## share file with Tong and Maike:
# write_csv(ecofp, file = "eco_footprint_processed.csv")
```
